Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-04-02 paper/manuscript.Rmd
stretch width fig 2 in doc

```{r, fig.cap = '(ref:fig1)', fig.width=4.5}
knitr::include_graphics('../graphics/IMG_1562_crop.JPG')
```

@@

```{r, fig.cap = '(ref:fig2)'}
knitr::include_graphics('../graphics/Fig2.png')
```

>>>>

```{r, fig.cap = '(ref:fig1)', fig.width=4}
knitr::include_graphics('../graphics/IMG_1562_crop.JPG')
```

@@

```{r, fig.cap = '(ref:fig2)', fig.width=4}
knitr::include_graphics('../graphics/Fig2.png')
```
